The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-16 talk/vmil2012/paper.tex
Add PyPy and RPython to acknowledgements
tweaks to the introduction

Besides being common, guards have various costs attached to them.
Guards have a runtime cost, they take time to execute. Therefore it is
important to make the on-trace execution of guards as efficient as possible. On
the other hand, guards are possible deoptimization points. The recorded and
compiled path has to be left if a guard fails, returning control to the
interpreter. Therefore guards need enough associated information to enable
rebuilding the interpreter state. The memory overhead of this information
should be kept low. These constraints and trade-offs are what make the design
and optimization of guards an important and non-trivial aspect of the construction
of a tracing just-in-time compiler.

%Section~\ref{sec:Evaluation} presents Figures about the absolute number of
%operations for each benchmark, and the overhead produced by the information
%stored at the different levels for the guards
In this paper we want to substantiate the aforementioned observations and
describe based on them the reasoning behind the implementation of guards in
RPython's tracing just-in-time compiler. the contributions of this paper are:
\begin{itemize}
  \item an analysis and benchmark of guards in the context of RPython's tracing JIT,
  %An analysis of guards in the context of RPython's tracing JIT to
  %substantiate the aforementioned observation, based on a set of benchmarks,
  \item detailed measurements about the frequency and the
  overhead associated with guards, and
  \item a description about how guards are implemented in the high\-
  and low-level components of the JIT and describe the rationale behind the design
\end{itemize}

@@

\section*{Acknowledgements}
We would like to thank David Edelsohn, Samuele Pedroni and Stephan Zalewski for their helpful
feedback and valuable comments while writing this paper.

>>>>

Besides being common, guards have various costs associated to them.
Guards have a runtime cost, they take time to execute. Therefore it is
important to make the on-trace execution of guards as efficient as possible. On
the other hand, guards are possible deoptimization points. The recorded and
compiled path has to be left if a guard fails, returning control to the
interpreter. Therefore guards need enough associated information to enable
rebuilding the interpreter state. The memory overhead of this information
should be kept low. These constraints and trade-offs are what makes the design
and optimization of guards an important and non-trivial aspect of the construction
of a tracing just-in-time compiler.

%Section~\ref{sec:Evaluation} presents Figures about the absolute number of
%operations for each benchmark, and the overhead produced by the information
%stored at the different levels for the guards
In this paper we want to substantiate the aforementioned observations about guards and
describe based on them the reasoning behind their implementation in
RPython's tracing just-in-time compiler. the contributions of this paper are:
\begin{itemize}
  \item an analysis and benchmark of guards in the context of RPython's tracing JIT,
  %An analysis of guards in the context of RPython's tracing JIT to
  %substantiate the aforementioned observation, based on a set of benchmarks,
  \item detailed measurements about the frequency and the
  overhead associated with guards, and
  \item a description about how guards are implemented in the high\-
  and low-level components of the JIT and describe the rationale behind the design
\end{itemize}

@@

\section*{Acknowledgements}
We would like to thank David Edelsohn, Samuele Pedroni and Stephan Zalewski for their helpful
feedback and valuable comments while writing this paper.
We thank the PyPy and RPython community for their continuous support and work:
Armin Rigo, Antonio Cuni, Maciej Fijałkowski, Samuele Pedroni, and countless
others. Any remaining errors are our own.
